---
title: "HW4"
author: "Jally"
date: "October 6, 2016"
output: html_document
---
## Question 1
## Create the vectors
```{r}
c(1:20)# Create the vector (1,2,3,...,19,20)

c(20:1)# Create the vector (20,19,...,2,1) 

c(1:20,19:1)# Create the vector (1,2,3,...,19,20,19,18,...,2,1)

tmp<-c(4,6,3)# Create the vector (4, 6, 3) and assign it to the name tmp

rep(tmp,10)# Create the vector (4,6,3, 4,6,3,...,4,6,3) where there are 10 occurrences of 4

rep(tmp,10,len=31)# Create the vector (4,6,3, 4,6,3,...,4,6,3,4) where there are 11 occurrences of 4, 10 occurrences of 6 and 10 occurrences of 3

rep(tmp,c(10,20,30))# Create the vector (4,4,...,4,6,6,...,6,3,3,...,3) where there are 10 occurrences of 4,20 occurrences of 6 and 30 occurrences of 3
```

## Question 2
## Create a vector of the values of  at x=3,3.1,3.2,...,5.9,6.
```{r}
x<-seq(3,6,by=0.1) #create a vector x=3,3.1,3.2,...,5.9,6
exp(x)*cos(x) #create the vector of e^x*cos(x)
```

## Question 3
## create the vectors
```{r}
(0.1^seq(3,36,by=3))*(0.2^seq(1,34,by=3))#create a vector (0.1^3*0.2^1,0.1^6*0.2^4,0.1^9*0.2^7,...,0.1^36*0.2^34)

(2^(1:25))/(1:25) #create a vector  (2,2^2/2,...2^25/25)
```

## Question 4
## Calculate the following formula
```{r}
a <- 10:100 #create a vector (10,11,...,100)
sum(a^3+4*a^2) # caculate the sum of formula

b <- 1:25 # create a vector (1,2,...,25)
sum((2^b)/b + (3^b)/(b^2))#caculate the sum of formula
```

## Question 5
## Use the function paste to create the following character vectors of length 30
```{r}
paste("label",1:30) # create character vectors ("label1","label2",.....,"label30").Notethatthereisasinglespace between label and the number following

paste("fn",1:30,sep="") # create character vectors ("fn1", "fn2", ..., "fn30"). In this case, there is no space between fn and the number following
```

## Question 6
## Execute the following lines which create two vectors of random integers which are chosen with replacement from the integers 0, 1, . . . , 999. Both vectors have length 250
```{r}
set.seed(50)
xVec <- sample(0:999, 250, replace=T)
yVec <- sample(0:999, 250, replace=T) 
#Suppose x = (x1,x2,...,xn) denotes the vector xVec and y = (y1,y2,...,yn) denotes the vector yVec

yVec[-1] - xVec[-length(xVec)] #Create the vector (y2-x1,y3-x2,...yn-xn-1)

sin(yVec[-length(yVec)]) / cos(xVec[-1]) #Create the vector(sin(y1)/cos(x2),...sin(yn-1))/cos(xn)

xVec[-c(249,250)] + 2*xVec[-c(1,250)]-xVec[-c(1,2)] #Create the vector (x1+2*x2-x3,...x(n-2)+2*x(n-1)-xn)

sum(exp(-xVec[-1])/(xVec[-length(xVec)]+10))
```

## Question 7
## This question uses the vectors xVec and yVec created in the previous question and the functions sort, order, mean, sqrt, sum and abs
```{r}
yVec[yVec>600] #Pick out the values in yVec which are>600.

(1:length(yVec))[yVec>600] # pick out the index positions in yVec of the values which are > 600

xVec[yVec>600] # pick out values in xVec which correspond to the values in yVec which are > 600? (By correspond, we mean at the same index positions.)

sqrt(abs(xVec-mean(xVec))) # Create the vector ( |x1 âˆ’ ð‘¥|1/2, |x2 âˆ’ ð‘¥|1/2, . . . , |xn âˆ’ ð‘¥|1/2) where ð‘¥ denotes the mean of the vector x = (x1,x2,...,xn)

sum(yVec>max(yVec)-200) # caculate how many values in yVec are within 200 of the maximum value of the terms in yVec

sum(xVec %% 2 == 0 ) # caculate how many numbers in xVec are divisible by 2

xVec[order(yVec)] # Sort the numbers in the vector xVec in the order of increasing values in yVec

yVec[seq(1,length(yVec),by=3)] #Pick out the elements in yVec at index positions 1,4,7,10,13,...

```

## Question 8
## By using the function cumprod or otherwise,calculate: 1+2/3+2*4/(3*5)+...+(2*4*...*38)/(3*5*...*39)
```{r}
1+sum(cumprod(seq(2,38,by=2)/seq(3,39,by=2)))
```